On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-11-13 paper.tex
Fig 1 added (summary)
In Fig. 1, I summarized the results obtained so far.

\section{Introduction}

@@

\section{Preliminaries}
\input{uos_preliminaries.tex}

@@

>>>>

%------------------------------------------------------
	\section{Introduction}
%------------------------------------------------------

@@

\begin{figure}[tb]
\begin{tikzpicture}

\node (origin) at (0, 0) {};

\draw[-latex] (origin) -- ++(0:3) node[below] {$\delta$}; 
\node at (1, -0.2) {1};
\node at (2, -0.2) {2};
\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
\node at (-0.2, 1) {1};
\node at (-0.2, 2) {2};
\node at (-0.2, 3) {3};
\node at (-0.2, 4) {4};

%Results
\node at (1, 4) {$O(n^2)$};
\node at (1, 3) {$O(n)$};
\node at (1, 2) {$O(n^2)$};
\node at (1, 1) {$O(n)$ \cite{DemaineDNA24}};

\node at (2, 1) {$O(n^2)$};

\end{tikzpicture}
\caption{Summary of the results.}
\label{fig:summary}
\end{figure}

%------------------------------------------------------
	\section{Preliminaries}
%------------------------------------------------------
\input{uos_preliminaries.tex}

@@

\section{Problem description}

In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
We consider this finiteness problem under various settings of the values of delay and arity. 
Results on this problem are summarized in Fig.~\ref{fig:summary}.
